A Methodology and Implementation of Automated Emissions Harmonization for Use in Integrated Assessment Models

### 2017-06-09 meth.tex
more shinichiro edits

\subsection{\code{aneris} Workflow}\ref{label:workflow}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=0.85\textwidth]{regions.png}
    \caption[]{
      \label{fig:regions}
      The 5 regions used in the RCPs with their 11-region constituents: Asia
      (Central Asia, South Asia, Pacific Asia), Latin Ameria, the Middle East
      and Africa, the OECD (North America, Western Europe, and Pacfic OECD),
      Reforming Economies (Eastern Europe and Former Soviet Union).
    }
  \end{center}
\end{figure}

>>>>

\subsection{\code{aneris} Workflow}\label{sec:workflow}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=0.85\textwidth]{regions.png}
    \caption[]{
      \label{fig:regions}
      The 5 regions used in the RCPs with their 11-region constituents: Asia
      (Central Asia, South Asia, Pacific Asia), Latin America, the Middle East
      and Africa, the OECD (North America, Western Europe, and Pacific OECD),
      Reforming Economies (Eastern Europe and Former Soviet Union).
    }
  \end{center}
\end{figure}

### 2017-06-09 results.tex
more shinichiro edits

In order to test the \code{aneris} harmonization procedure, results from the IAM
MESSAGE-GLOBIOM \cite{fricko_marker_2017} was processed. Two scenarios from the
SSP scenario library \cite{Riahi2017153,Rao2017346} are investigated. The SSP2,
or ``middle of the road'', scenario family is chosen to be analyzed because
MESSAGE-GLOBIOM is the marker scenario for this SSP. Of all SSP2 scenarios, the
reference (marker) and SSP2-45 scenarios are analyzed. Notably, emissions from
multiple sectors tend to increase in the reference scenario, thus testing the
harmonization mechanism with an increasing emissions pathway. The SSP2-45
scenario, where the ``45'' designation refers to a scenario with end-of-century
emissions resulting in approximately a 4.5 $\frac{\text{W}}{\text{m}^2}$
radiative forcing due to both warming from GHGs and fluoridated gases as well as
cooling from aerosols, is chosen because mitigation technologies and policies
are enacted causing a general reduction in pollutants and GHGs, including
(eventual) negative CO2 emissions in some regions and sectors due to carbon
capture and sequestration and afforestation. This scenario explores the
harmonization mechanism's response to generally decreasing emission
trajectories.

MESSAGE-GLOBIOM includes a representation of 11 distinct regions which can be
mapped directly to the 5-region definition used in the RCPs. Historical data is
taken from previously described LUC and anthropogenic sources, which comprise 10
separate pollutant and GHG species and 13 sectors. Therefore, a total of 1430
distinct trajectories were harmonized for each scenario.

The effect of harmonization overrides is analyzed by harmonizing each scenario
first without and then with overrides. Of the 1430 trajectories, approximately
2\% required the use of harmonization overrides after an initial investigation;
thus, 98\% of all trajectories were satisfactorily determined using the default
methods as chosen by the harmonization algorithm. Figure \ref{fig:nox} provides
one such example of a emissions species and sector in which all regions were
satisfactorily harmonized with the default methods. As can be seen, results with
and without overrides are identical.

>>>>

In order to test the \code{aneris} harmonization procedure, results from the IAM
MESSAGE-GLOBIOM \cite{fricko_marker_2017} was processed. Two scenarios from the
SSP scenario library \cite{Riahi2017153,Rao2017346} are investigated. The SSP2,
or ``middle of the road'', scenario family is chosen to be analyzed because
MESSAGE-GLOBIOM is the marker scenario for this SSP. Of all SSP2 scenarios, the
reference (marker) and SSP2-45 scenarios are analyzed. Notably, emissions from
multiple sectors tend to increase in the reference scenario, thus testing the
harmonization mechanism with an increasing emissions pathway. The SSP2-45
scenario, where the ``45'' designation refers to a scenario with end-of-century
emissions resulting in approximately a 4.5 $\frac{\text{W}}{\text{m}^2}$
radiative forcing due to both warming from GHGs and fluoridated gases as well as
cooling from aerosols, is chosen because mitigation technologies and policies
are enacted causing a general reduction in pollutants and GHGs, including
(eventual) negative CO2 emissions in some regions and sectors due to carbon
capture and sequestration and afforestation. This scenario explores the
harmonization mechanism's response to generally decreasing emission
trajectories.
% * <sfujimori112256@gmail.com> 2017-06-07T10:22:28.473Z:
% 
% As a supplementary, it would be better to show the total kyoto gases emissions for these two scenarios, which gives readers rough image what kind of scenarios we choose.
% 
% ^.

MESSAGE-GLOBIOM includes a representation of 11 distinct regions which can be
mapped directly to the 5-region definition used in the RCPs. Historical data is
taken from previously described LUC and anthropogenic sources, which comprise 10
separate pollutant and GHG species and 13 sectors shown in
\ref{tab:sp}. Therefore, a total of 1430 distinct trajectories were harmonized
for each scenario.

\begin{table}[]
  \centering
  \caption{Harmonized Species and Sectors}
  \label{tab:sp}
  \begin{tabular}{|l|l|}
    \hline
    \textbf{Emissions Species}        & \textbf{Sectors}                    \\
    \hline
    Black Carbon (BC)                 & Agricultural Waste Burning          \\
    Hexafluoroethane (C2F6)           & Agriculture                         \\
    Tetrafluoromethane (CF4)          & Aircraft                            \\
    Methane (CH4)                     & Energy Sector                       \\
    Carbon Dioxide (CO2)              & Forest Burning                      \\
    Carbon Monoxide (CO)              & Grassland Burning                   \\
    Hydrofluorocarbons (HFCs)         & Industrial Sector                   \\
    Nitrous Oxide (N2O)               & International Shipping              \\
    Ammonia (NH3)                     & Residential Commercial Other        \\
    Nitrogen Oxides (NOx)             & Solvents Production and Application \\
    Organic Carbon (OC)               & Transportation Sector               \\
    Sulfur Hexafluoride (SF6)         & Unharmonized                        \\
    Sulfur Oxides (SOx)               & Waste                               \\
    Volatile Organic Compounds (VOCs) &                                     \\
    \hline
  \end{tabular}
\end{table}

The effect of harmonization overrides is analyzed by harmonizing each scenario
first without and then with overrides. Of the 1430 trajectories, approximately
10\% were reported as a diagnostic (see Section \ref{sec:workflow}) of which 2\%
required the use of harmonization overrides after an initial investigation;
thus, 98\% of all trajectories were satisfactorily determined using the default
methods as chosen by the harmonization algorithm. Figure \ref{fig:nox} provides
one such example of a emissions species and sector in which all regions were
satisfactorily harmonized with the default methods. As can be seen, results with
and without overrides are identical.
